Project Thesis/Report

### 2022-01-03 Gandhi_Project_Report/draft1.tex
cleaning git

\documentclass[12 pt]{article}
\usepackage[utf8]{inputenc}
\usepackage{filecontents}
\usepackage[many]{tcolorbox}
\usepackage{graphicx}
\usepackage{harpoon}
%\usepackage{apacite} 
\usepackage{xcolor}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mdframed}
%\usepackage[authoryear]{natbib}
\usepackage{hyperref, url}
\usepackage[show]{ed}
\usepackage{subfigure}
\usepackage[ntheorem]{empheq} 
\usepackage{amsthm, amssymb, amsfonts, latexsym}
\usepackage{pst-all}

@@

@@

%%%% PNAS GRAPHICS SETUP- FROM THE PNAS STYLE LATEX FILE
\RequirePackage{graphicx,xcolor}
\RequirePackage{colortbl}
\RequirePackage{booktabs}
\RequirePackage{algorithm}
\RequirePackage[noend]{algpseudocode}
\RequirePackage{changepage}
\RequirePackage[twoside,%
				letterpaper,includeheadfoot,%
				layoutsize={8.125in,10.875in},%
                layouthoffset=0.1875in,%
                layoutvoffset=0.0625in,%
                left=38.5pt,%
                right=43pt,%
                top=43pt,% 10pt provided by headsep
                bottom=32pt,%
                headheight=0pt,% No Header
                headsep=10pt,%
                footskip=25pt,
                marginparwidth=38pt]{geometry}
\RequirePackage[labelfont={bf,sf},%
                labelsep=period,%
                figurename=Fig. ]{caption}
\setlength{\columnsep}{13.5pt} % Distance between the two columns of text
\setlength{\parindent}{12pt} % Paragraph indent

@@

\externaldocument{Supp_Koopman-0808}
\begin{document}

@@

\section{Introduction}\label{ch1}

@@

\section{Discrete-time Dynamical Systems}\label{ch2}

% In this chapter, we provide a brief description of what a discrete-time dynamical system is and what it means for it to exhibit chaos. We refer to \cite{devaney2018introduction, de2013elements} for more details.

@@

% \subsection{Invariant Sets}

@@

% \subsection{Chaos}

@@

% \subsection{Conjugacy}

@@

\section{The Learning Problem}\label{ch3}

@@

\subsection{Taken Embedding Theorem} \label{subs_TakensEmbedding}

@@

% \subsection{Obstacles to Takens}
% Despite the fact that the Takens' Embedding Theorem is a powerful result and provides compelling reason to believe that it is possible to accurately ()\emph{right word?}) reconstruct the underlying space, it does present some serious limitations:
% \vspace{-5mm}
% \begin{enumerate}
% \item Even if we can indeed find \Ftheta{}  our \emph{approximation} of \Ftheta{}  is a map from a larger set $\mathbb{R}^{2m+1}$ containing the embedded attractor. There are, however, no theoretical guarantees that \Ftheta{}  will keep this attractor $U$  the same.(\textbf{We haven't properly said that U is an attractor, or have we.})
% \item Takens only holds for noiseless observations. Suppose the case where \Ftheta{} was learnt, but due to measurement error or other noise we obtained the set $V$ and not the original attractor. Due to the chaotic nature of the underlying system (i.e. the fact that it has SIDC), this new system $V$ will then move in a different direction. This problem will later be eliminated by some properties of a new function $g$, namely the Unique Solution Property. 
% \item It is an unfortunate case that the functional complexity (i.e., the relative number of oscillatory graphs \cite{manjunath2021universal}) as well as stability of the embedding \Ftheta{} (\textbf{cite?})depends on the choice of observable $\theta$. This means that we may even learn a map that complicates our learning task and in so doing adds obstacles to the road to learning a conjugate map with predictive power. (\textbf{Am I talking nonsense here?})
% \end{enumerate}

@@

% \textbf{Explanation continued here}

@@

% \textbf{Continue explaining here}
\newpage

\section{Driven Dynamical Systems to Forecast Problems} \label{ch4}

In this chapter, we discuss results pertaining to the mapping of temporal data obtained from a discrete-dynamical system onto a different space through the notion of a driven dynamical system. 
We also consider the conditions a driven system should have to avoid adding distortion to its state space representation, as well as then ensuring that the single-delay dynamics (SDD) are conjugate (or at least semi-conjugate to the system). 
The SDD can then be used to forecast and reconstruct the underlying attractor. \textbf{Is this attractor assumed to exist?}

\subsection{Nonautonomous and Driven Dynamical Systems}

A nonautonomous dynamical system is simply a dynamical system (as defined before in \textbf{link to above}) where the input $u$ from the input space $U$, a  topological space, is time-dependent. \textbf{This means it can no longer be generated by a flow?}

@@

\subsection {Unique Solution Property}

@@

\emph{(More discussion on USP?)}

Having already defined the reachable set $X_U$, we pause for a moment to fix additional notation.
Letting $\cev{u}^{n}:=(\ldots,u_{n-2} ,u_{n-1})$ be the left-infinite subsequence of an input, $\overleftarrow{U}$ then denotes all these left-infinite sequences in $U$. 
Moreover, $\cev{u}^{n}v:=(\ldots,u_{n-2} ,u_{n-1}, v)$ is to symbolise the input up to time $n$ with $v \in U$ being the specific input value at time $n$. 
The introduction of a new input at time $n$ can be described by a mapping $\sigma_v:   \cev{u}^{n} \mapsto \cev{u}^{n}v$.

@@

Re-sketching the graph\ref{Scomm_h} above by fixing the input $v$ in $g$ and replacing $X_U$ by its left-infinite sequence space $\overleftarrow{U}$, we obtain the graph below. In this case, the function $H:\overleftarrow{U}\to\overleftarrow{X}_U$, a map that is both continuous and surjective, is called a \emph{causal mapping}.

\begin{Definition}
  [\bf Causal Mapping]\label{Def_CausMap}
  A continuous, surjective map $H:\overleftarrow{U}\to\overleftarrow{X}_U$ such that \[H\circ\tilde{g}_v=\sigma\circ{H}\] where $\tilde{g}_v$ maps $(\ldots, u_{-2}, u_{-1})$ to $(\ldots, u_{-2}, u_{-1}, g(v, u_{-1}))$.
\end{Definition}

@@

\begin{Theorem}
  The following statements are equivalent:
  \vspace{-8mm}
  \begin{enumerate}[noitemsep, label=\roman*.]
    \item $g$ has the USP. 
    \item $g$ is a topological contraction.
  \end{enumerate}
\end{Theorem}
\begin{proof}
  (postponed)  [11] eqn.6 
\end{proof}

@@

\subsection {Choosing the driven system $g$}

@@

When a causal embedding $H$ exists for the driven system $g$, one can map an arbitrary input ${u}$ onto the solution space $X$ without additional distortion or information-loss.  \textbf{(Cite.)} 
When an embedding is established, the question of possible additional complexity in the solution is removed by guaranteeing that, since the systems are conjugate (semi-conjugate, (refer)), $g$ does not add any (some) complexity to the system.  
It is, however, a balancing act as it also undesirable to choose a function $g$ that quenches the temporal structure in $u$ by contracting to such a degree that the ability to recover information from the original system is lost completely. 
To obtain a suitably complex function $g$, it is desired that the the reachable set of a driven system  be large enough to relate to the input.  \textbf{(Expand here. It stops a bit abruptly.)}

In the example above (\ref{ex_halfux}), the input's temporal variation cannot be related to the reachable set as $X_U$ consists of a single element and so little, if not no, information is encoded.  Rather, the reachable set of a driven system must therefore be such that the inverse-limit space of $U_T$ can be embedded in some finite self-product of the reachable set of $T$ \textbf{(refer or cite)}. To this end, consider the notion of State-Input (SI) Invertibility.

@@

\textbf{Explain more here.}

We make special note of a specific driven system. The function 
\begin{equation}  \label{eqn_driving}
g(u,x)=(1-a)x+a{\cdot}tanh(Au+\alpha{a}Bx)
\end{equation} 
is both SI-invertible and possesses the USP. The proof of these two facts is rather involved and  hence the proof, instead of being replicated here, may be found in \textbf{(cite relevant article)}
This specific driving function $g$ is used in our implementation and is more completely discussed in chapter \ref{sect5}

@@

This definition is stated in a not completely rigourous manner as the more formal definition makes use of processes, a concept which would take some time to establish and detracts from the principal thrust of this paper/project/thesis.

\textbf{Is it VERY obvious to the reader at this point what the general 'thrust' of the paper IS?} \textbf{Cite articles}

@@

This also solves the problem of perturbation/noise introduced by the observable or measurement function. Recall from before that an observable is inherently a map that discretises the underlying continuous-time system. Moreover, measurement and device error introduce mistakes. Since we are working with a chaotic system displaying sensitive dependence on initial conditions, these small errors could potentially send the trajectory into a completely different attractor. In the presence of the UAP, however, small measurement errors introduced into the system do not pose the same danger as before.

\textbf{(Rephrase and/or expand)}

\subsection{The next step in Dynamics}

@@

The following theorem establishes the existence of a well-defined map $G_T$ describing the single-delay dynamics of the system above.

@@

\begin{Definition}
  The inverse-limit space $\widehat{U}_T$, a subspace of $\overleftarrow{U}$, is defined by $$\widehat{U}_T:=\{(\ldots, u_{-2}, u_{-1}):T(u_n)=u_{n+1}\}$$ This space is well-defined since $T:U\to{U}$ is surjective by assumption. \textbf{Expand why}
\end{Definition}

@@

\begin{equation}
  %  \[ 
      \psset{arrows=->, arrowinset=0.25, linewidth=0.6pt, nodesep=3pt, labelsep=2pt, rowsep=0.7cm, colsep = 1.1cm, shortput =tablr}
      \everypsbox{\scriptstyle}
      \begin{psmatrix}
      \widehat{U}_T  && \widehat{U}_T \\
      Y_T && Y_T \\
      %%%
     %  \ncline{1,1}{1,2}^{\widehat{T}} \ncline{1,1}{2,1} <{h}
     %  \ncline{1,2}{2,2} > {H_2}
     %  \ncline{2,1}{2,2}^{G_T}
      \end{psmatrix}
    %  \]
    \end{equation}

@@

\subsubsection*{Summarising the discussing thus far:}

@@

One can therefore learn the single-delay lag dynamics of the driven system states via $G_T$ with enough data thanks to the USP/UAP. This enables us to do at least 2 things: 
\vspace{-8mm}
\begin{itemize}
\item Forecast future values of $x_n$ via iterates of $G_T$ (as $G_T$ can be determined.
\item Forecast future values of $u_n$. 
\end{itemize}

\subsection{A discussion of $G_T$ }

By establishing the existence of the map $G_T$, we’ve essentially embedded the attractor $U$ \textbf{(So far we haven't really spoken about an attractor)} into the higher dimensional space $X\times{X}$. \textbf{(Why is it true that it's higher-dimensional?)}
In layman’s terms, this ensures that there is more “dimensional room” for the underlying system’s underlying dynamics to “move”. As the dynamics aren’t as “squashed”, we might therefore hope that the dynamics of $G_T$ are in some sense simpler than that of $T$. (Taken note of the fact that $G_T$ is a homeomorphism even when $T$ is just continuous)

In \emph{[Koopman]} it is illustrated in an empirical fashion in that the map $G_T$ describes dynamics which are less functionally complex than that of $T$ or of the map $\Phi_{2d,\theta}$ (as discussed above in the section on Takens). This is done by implementing a Recurrent Neural Network (RNN), but not discussed as of yet. \emph{(Add in that we'll be using Pearson coefficient?)}

We opt to learn $G_T$ in an indirect manner by defining a new map $\Gamma$. It follows immediately from $G_T$’s existence that $\Gamma$ also exists.

The reasons for taking this roundabout approach remain to be discussed, but a pat answer may be immediately given: When we have learnt $\Gamma$, we can drive the system autonomously and then we know $G_T$ anyway.

\begin{Theorem}
  When $x_n$ and $x_{n-1}$ are successive points on a solution obtained for input-orbit of $T$ $\{u_n\}$, then the map $\Gamma: X\times{X}\to{U}$ defined by $(x_{n-1},x_n)\mapsto{u_n}$ exists whenever $G_T$ exists [Koopman, Theorem 3c] 
\end{Theorem}

\begin{Definition}
 The projection mapping $\pi_i$ is defined as follows: $$\pi_1:(a_1,a_2)\to{a_1}$$ and $$\pi_2:(a_1,a_2)\to{a_2}$$ 
\end{Definition}

We now have the graph below:

\begin{figure}[ht]
  \includegraphics[scale=0.3]{gammatemp.png}
  \centering
  \label{fig:conjugacy_with_Gamma}
\end{figure}

And a final set of equations - equations that have been constructed from data!
\begin{eqnarray}
	u_{k+1} &=& \pi_1 \circ (\Gamma, \pi_2) \circ (\pi_2,g) (u_k,x_k) \label{Seqn_u}\\
	x_{k+1} &=& \pi_2 \circ (\Gamma, \pi_2) \circ (\pi_2,g) (u_k,x_k). \label{Seqn_x}
\end{eqnarray}

The problem thus simplifies to the issue of learning the map $\Gamma$ and combining this with the projection mapping $\pi_2$ and the function $g$, which will be known.

\subsection{Advantages of learning $\Gamma$}

Why are we going such a lengthy roundabout route, one may immediately ask. Why not just learn the map $G_T$ from the get-go? On the surface, this seems to be an arbitrarily chosen path with no real reason for the choice made, so we take a pause again and discuss our reasoning for learning Gamma.
There are a number of distinct advantages.

Learning $\Gamma$ saves computational resources. This follows from the fact that the input $u_n$ at time $n$ lies in a low-dimensional subspace of the high-dimensional subspace $X\times{X}$ due to the fact that it is zero-padded.

Input- and parameter-related stability is achieved if $g$ has the USP
\newline \emph{Define the two types of stabilities}
\newline \emph{Sentence on $u$, $v$, tails, USP and product topology}
\newline If we opt to work with $Y-T$, errors can occur. \emph{Expand}
\newline $\Gamma$ is more stable. \emph{Explain why}

Global dissipativity prevents large numerical errors due to input data. $\Gamma$ is globally dissipative (\emph{Define}) whereas $G_T$ is not guaranteed to be. IF we were to rather learn $G_T$, we would risk having exactly the same problems arise that could arise also for Takens. \textbf{\emph{ADD THIS TO ERRORS IN TAKENS: NOT GUARANTEED GLOBALLY DISSIPATIVE}}
\newline \emph{Expand here ...}

\emph{Where to add:If $g$ has USP, then any solution to $g$ is a non-autonomous uniform attractor}

@@

\section{Implementation} \label{sect5}

>>>>

% \documentclass[12 pt]{article}
\documentclass[a4paper,12pt,twoside]{book}
\pagestyle{headings}
\usepackage[utf8]{inputenc}
\usepackage{filecontents}
\usepackage[many]{tcolorbox}
\usepackage{graphicx}
\usepackage{harpoon}
%\usepackage{apacite} 
\usepackage{xcolor}
\usepackage{latexsym}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{mdframed}
%\usepackage[authoryear]{natbib}
\usepackage{hyperref, url}
\usepackage[show]{ed}
\usepackage{subfigure}
\usepackage[ntheorem]{empheq} 
\usepackage{amsthm, amssymb, amsfonts, latexsym}
% \usepackage{pst-all}

@@

\usepackage{pst-node}

@@

%%%% PNAS GRAPHICS SETUP- FROM THE PNAS STYLE LATEX FILE
\RequirePackage{graphicx,xcolor}
\RequirePackage{colortbl}
\RequirePackage{booktabs}
\RequirePackage{algorithm}
\RequirePackage[noend]{algpseudocode}
\RequirePackage{changepage}
\RequirePackage[twoside,%
				letterpaper,includeheadfoot,%
				layoutsize={8.125in,10.875in},%
                layouthoffset=0.1875in,%
                layoutvoffset=0.0625in,%
                left=38.5pt,%
                right=43pt,%
                top=43pt,% 10pt provided by headsep
                bottom=32pt,%
                headheight=0pt,% No Header
                headsep=30pt,%
                footskip=25pt,
                marginparwidth=38pt]{geometry}
\RequirePackage[labelfont={bf,sf},%
                labelsep=period,%
                figurename=Fig. ]{caption}
\setlength{\columnsep}{13.5pt} % Distance between the two columns of text
\setlength{\parindent}{12pt} % Paragraph indent

@@

% \externaldocument{Supp_Koopman-0808}
\begin{document}

@@

\tableofcontents

% \chapter{Introduction}\label{ch1}

@@

% \chapter{Discrete-time Dynamical Systems}\label{ch2}

% In this chapter, we provide a brief description of what a discrete-time dynamical system is and what it means for it to exhibit chaos. We refer to \cite{devaney2018introduction, de2013elements} for more details. \label{Dfn_DS}

@@

% \section{Invariant Sets}

@@

% \section{Chaos}

@@

% \section{Conjugacy}

@@

% \chapter{The Learning Problem}\label{ch3}

@@

% \section{Taken Embedding Theorem} \label{sect_TakensEmbedding}

@@

% \section{Obstacles to Takens}
% Despite the fact that the Takens' Embedding Theorem is a powerful result and provides compelling reason to believe that it is possible to accurately ()\emph{right word?}) reconstruct the underlying space, it does present some serious limitations:
% \vspace{-5mm}
% \begin{enumerate}
% \item Even if we can indeed find \Ftheta{}  our \emph{approximation} of \Ftheta{}  is a map from a larger set $\mathbb{R}^{2m+1}$ containing the embedded attractor. There are, however, no theoretical guarantees that \Ftheta{}  will keep this attractor $U$  the same.(\textbf{We haven't properly said that U is an attractor, or have we.})
% \item Takens only holds for noiseless observations. Suppose the case where \Ftheta{} was learnt, but due to measurement error or other noise we obtained the set $V$ and not the original attractor. Due to the chaotic nature of the underlying system (i.e. the fact that it has SIDC), this new system $V$ will then move in a different direction. This problem will later be eliminated by some properties of a new function $g$, namely the Unique Solution Property. 
% \item It is an unfortunate case that the functional complexity (i.e., the relative number of oscillatory graphs \cite{manjunath2021universal}) as well as stability of the embedding \Ftheta{} (\textbf{cite?})depends on the choice of observable $\theta$. This means that we may even learn a map that complicates our learning task and in so doing adds obstacles to the road to learning a conjugate map with predictive power. (\textbf{Am I talking nonsense here?})
% \end{enumerate}

@@

% \emph{ADD THIS TO ERRORS IN TAKENS: NOT GUARANTEED GLOBALLY DISSIPATIVE}
% \textbf{Explanation continued here}

@@

% \textbf{Continue explaining here}
% \newpage

\chapter{Driven Dynamical Systems to Forecast Problems} \label{ch4}

In this chapter, we discuss results pertaining to the mapping of temporal data obtained from a discrete-dynamical system onto a different space through the notion of a driven dynamical system. 
We also consider the conditions a driven system should have to avoid adding distortion to its state space representation, as well as then ensuring that the single-delay dynamics (SDD) are conjugate (or at least semi-conjugate to the system). 
The SDD can then be used to forecast and reconstruct the underlying attractor. \ednote{Is this attractor assumed to exist?}

\section{Nonautonomous and Driven Dynamical Systems}

A nonautonomous dynamical system is simply a dynamical system (as defined before in \ref{Dfn_DS}) where the input $u$ from the input space $U$, a  topological space, is time-dependent.

@@

\section {Unique Solution Property}

@@

One of the first result obtained upon defining the USP, is the fact that every solution will attract any different initial conditions towards the component parts of the solution, i.e. that the solution $\Psi$ is a non-autonomous uniform attractor. \ednote{Define Uniform Attractor before stating theorem.}

\begin{Theorem} \label{Thm_AttractorSoln}
  If $g$ has USP, then any solution to $g$ is a non-autonomous uniform attractor 
\end{Theorem}
\begin{proof}
  \cite{Manju_Nonlinearity}
\end{proof}

\ednote{Additional discussion on USP?} 
Having already defined the reachable set $X_U$, we pause for a moment to fix additional notation.
Letting $\cev{u}^{n}:=(\ldots,u_{n-2} ,u_{n-1})$ be the left-infinite subsequence of an input, $\overleftarrow{U}$ then denotes all these left-infinite sequences in $U$. 
Moreover, $\cev{u}^{n}v:=(\ldots,u_{n-2} ,u_{n-1}, v)$ is to symbolise the input up to time $n$ with $v \in U$ being the specific input value at time $n$. 
The introduction of a new input at time $n$ can be described by a mapping $\sigma_v:   \cev{u}^{n} \mapsto \cev{u}^{n}v$.

@@

Re-sketching the graph\ref{Scomm_h} above by fixing the input $v$ in $g$ and replacing $X_U$ by its left-infinite sequence space $\overleftarrow{U}$, we obtain the graph below. In this case, the function $H:\overleftarrow{U}\to\overleftarrow{X}_U$, a map that is both continuous and surjective, is called a \emph{causal mapping}. 
make special note of a 
\begin{Definition}
  [\bf Causal Mapping]\label{Def_CausMap}
  A continuous, surjective map $H:\overleftarrow{U}\to\overleftarrow{X}_U$ such that \[H\circ\tilde{g}_v=\sigma\circ{H}\] where $\tilde{g}_v$ maps $(\ldots, u_{-2}, u_{-1})$ to $(\ldots, u_{-2}, u_{-1}, g(v, u_{-1}))$.
\end{Definition}

@@

\begin{Theorem}
  The following statements are equivalent:
  \vspace{-8mm}
  \begin{enumerate}[noitemsep, label=\roman*.]
    \item $g$ has the USP. 
    \item $g$ is a topological contraction.
  \end{enumerate}
\end{Theorem}
\begin{proof}
  (postponed) 
\end{proof}

@@

\section {Choosing the driven system $g$}

@@

When a causal embedding $H$ exists for the driven system $g$, one can map an arbitrary input ${u}$ onto the solution space $X$ without additional distortion or information-loss.  \ednote{(Cite.)} 
When an embedding is established, the question of possible additional complexity in the solution is removed by guaranteeing that, since the systems are conjugate (semi-conjugate, (refer)), $g$ does not add any (some) complexity to the system.  
It is, however, a balancing act as it also undesirable to choose a function $g$ that quenches the temporal structure in $u$ by contracting to such a degree that the ability to recover information from the original system is lost completely. 
To obtain a suitably complex function $g$, it is desired that the the reachable set of a driven system  be large enough to relate to the input.  \ednote{(Expand here. It stops a bit abruptly.)}

In the example above (\ref{ex_halfux}), the input's temporal variation cannot be related to the reachable set as $X_U$ consists of a single element and so little, if not no, information is encoded.  Rather, the reachable set of a driven system must therefore be such that the inverse-limit space of $U_T$ can be embedded in some finite self-product of the reachable set of $T$ \ednote{(refer or cite)}. To this end, consider the notion of State-Input (SI) Invertibility.

@@

SI-invertibility promises that 'enough' information is retained when $g$ is chosen without introducing additional unwanted complexity. \ednote{Expand why this is true.}

It is worth taking note of a specific driven system. The function 
\begin{equation}  \label{eqn_driving}
g(u,x)=(1-a)x+a{\cdot}tanh(Au+\alpha{a}Bx)
\end{equation} 
is both SI-invertible and possesses the USP. The proof of these two facts is rather involved and  hence the proof, instead of being replicated here, may be found in \textbf{(cite relevant article)}
This specific driving function $g$ is used in our implementation and is more completely discussed in chapter \ref{sect5}

@@

This definition is stated in a not completely rigourous manner as the more formal definition makes use of processes, a concept which would take some time to establish and detracts from the principal thrust of this paper/project/thesis. 
\ednote{Is it VERY obvious to the reader at this point what the general thrust of the paper is?}

@@

This also solves the problem of perturbation/noise introduced by the observable or measurement function. Recall from before that an observable is inherently a map that discretises the underlying continuous-time system. Moreover, measurement and device error introduce mistakes. Since we are working with a chaotic system displaying sensitive dependence on initial conditions, these small errors could potentially send the trajectory into a completely different attractor. In the presence of the UAP, however, small measurement errors introduced into the system do not pose the same danger as before.
\ednote{(Rephrase and/or expand)}

\section{The next step in Dynamics}

@@

The following theorem establishes the existence of a well-defined map $G_T$ describing the single-delay dynamics(SDD) of the system above.

@@

\begin{Definition}
  [\bf Inverse-Limit Space]\label{Dfn_InvLimSpace}
  The inverse-limit space $\widehat{U}_T$, a subspace of $\overleftarrow{U}$, is defined by $$\widehat{U}_T:=\{(\ldots, u_{-2}, u_{-1}):T(u_n)=u_{n+1}\}$$ 
\end{Definition}

The inverse-limit space is well-defined since $T:U\to{U}$ is surjective by assumption. \ednote{Should I explain this in more details or am  I then over-simplifiying?}

@@

\begin{equation} \label{Fig_inverse_limsystem}
  %  \[ 
      \psset{arrows=->, arrowinset=0.25, linewidth=0.6pt, nodesep=3pt, labelsep=2pt, rowsep=0.7cm, colsep = 1.1cm, shortput =tablr}
      \everypsbox{\scriptstyle}
      \begin{psmatrix}
      \widehat{U}_T  && \widehat{U}_T \\
      Y_T && Y_T \\
      %%%
     %  \ncline{1,1}{1,2}^{\widehat{T}} \ncline{1,1}{2,1} <{h}
     %  \ncline{1,2}{2,2} > {H_2}
     %  \ncline{2,1}{2,2}^{G_T}
      \end{psmatrix}
    %  \]
  \end{equation}

@@

\section*{Summarising the discussing thus far:}

@@

One can therefore learn the SDD of the driven system states via $G_T$ with enough data thanks to the USP/UAP. This enables us to do at least 2 things: 
\vspace{-8mm}
\begin{itemize}[noitemsep]
\item Forecast future values of $x_n$ via iterates of $G_T$ (as $G_T$ can be determined.
\item Forecast future values of $u_n$. 
\end{itemize}

\section{A discussion of $G_T$ }

In the above sections, we established the map $G_T$ describing the SDD of a driven system. By establishing the existence of this map, we’ve essentially embedded the attractor $U$ \ednote{(So far we haven't really spoken about an attractor)} into the higher dimensional space $X\times{X}$. \ednote{(Why is it true that it's higher-dimensional?)}
In layman’s terms, this ensures that there is more “dimensional room” for the underlying system’s underlying dynamics to “move”. As the dynamics aren’t as “squashed”, we might therefore hope that the dynamics of $G_T$ are in some sense simpler than that of $T$. (Taken note of the fact that $G_T$ is a homeomorphism even when $T$ is just continuous)

In \cite{manjunath2021universal} it is illustrated in an empirical fashion in that the map $G_T$ describes dynamics which are less functionally complex than that of $T$ or of the map $\Phi_{2d,\theta}$. This is done by implementing a Recurrent Neural Network (RNN), but not discussed as of yet. \ednote{(Add in that we'll be using Pearson coefficient?)}

We opt to learn $G_T$ in an indirect manner by defining a new map $\Gamma:(x_{n-1},x_n)\mapsto{u_n}$. It will follow immediately from $G_T$’s existence that $\Gamma$ also exists.

The reasons for taking this roundabout approach remain to be discussed in \ref{subs_LearnGamma}, but a pat answer may immediately be given: When $\Gamma$ has been learnt, the system can be driven autonomously and then $G_T$ is known anyway. We formalise this with a theorem.

\begin{Theorem}
  When $x_n$ and $x_{n-1}$ are successive points on a solution obtained for input-orbit of $T$ $\{u_n\}$, then the map $\Gamma: X\times{X}\to{U}$ defined by $(x_{n-1},x_n)\mapsto{u_n}$ exists whenever $G_T$ exists 
\end{Theorem}
\begin{proof}
  From [Koopman, Theorem 3c] 
\end{proof}

Projection mappings $\pi_i$ are defined in the traditional meaning where a $k$-dimensionalvector is projected to it's $i^{th}$ component such that $$\pi_i:(a_1,a_2, \ldotp, a_{k-1}, a_k)\to{a_i}$$

% \begin{Definition}
%   [\bf Projection Mapping]\label{Dfn_ProjMap}
%  The projection mapping $\pi_i$ is defined as follows: $$\pi_1:(a_1,a_2)\to{a_1}$$ and $$\pi_2:(a_1,a_2)\to{a_2}$$ 
% \end{Definition}

The graph in equation \ref{Fig_inverse_limsystem} is then extended as below:

\begin{figure}[ht] \label{Fig_Gamma}
  \includegraphics[scale=0.3]{gammatemp.png}
  \centering
  \label{fig:conjugacy_with_Gamma}
\end{figure}

The problem finally simplifies to the issue of learning the map $\Gamma$ and combining this with the projection mapping $\pi_2$ and the function $g$, which will be known. A final set of equations is obtained - equations that have been entirely constructed from data.
\begin{eqnarray}
	u_{k+1} &=& \pi_1 \circ (\Gamma, \pi_2) \circ (\pi_2,g) (u_k,x_k) \label{Seqn_u}\\
	x_{k+1} &=& \pi_2 \circ (\Gamma, \pi_2) \circ (\pi_2,g) (u_k,x_k). \label{Seqn_x}
\end{eqnarray}

\section{Advantages of learning $\Gamma$} \label{subs_LearnGamma}

One may immediately ask why we opt to take such a roundabout route; why not just learn the map $G_T$ from the get-go? On the surface, this seems to be an arbitrary decision path with no real reasoning, so we take a pause again and discuss the motivation for learning Gamma.
There are a number of distinct advantages.

Learning $\Gamma$ saves computational resources. This is due to the fact that the input $u_n$ lies in a lower-dimensional subspace of the high-dimensional space $X\times{X}$. In practice, if the input is of a  lower dimension, one may easily embed it into the space $X\times{X}$ by padding the vector $u_n$ with zeroes.

\textbf{Can we discuss how to put this across well? I would like to add it in as I think it beneficial to the discussion.}

Moreover, two types of stability are achieved when $g$ has the USP.

Input- and parameter-related stability is achieved if $g$ has the USP
\newline \emph{Define/Explain the two types of stabilities}
\newline \emph{Sentence on $u$, $v$, tails, USP and product topology}
\newline If we opt to work with $Y_T$, errors can occur. Expand
\newline $\Gamma$ is more stable. Explain why.

Thirdly, $\Gamma$ is globally dissipative whereas $G_T$ is not guaranteed to be(\emph{Cite}). \ednote{Add linking sentence.} Global dissipativity prevents large numerical errors due to input data.

The $\omega$-limit set $\omega(u;T)$ of a point $u$ is defined to be the collection of limit points of the sequence $\{x,Tu,T^2u,\ldots\}$. This set is nonempty, and $\omega(u;T)$ is invariant. \textbf{(Change)}

\begin{Definition}
  [\bf Global Dissipativity]\label{Dfn_GlobalDiss}
	We say a dynamical system $(Z,f)$ is globally dissipative if there exists a nonempty proper closed subset $B$ of $Z$  so that for all $x\in Z\setminus B$, (i). $\omega(x;f) \subset B$  and (ii).  $B$ is positively invariant that is $f(B) \subset B$. We call any such closed subset $B$ a trapping set of $f$. 
\end{Definition}

If a system is not globally dissipative, neglibly small errors result in major errors which thus induce predictions to fail utterly. If one learns $G_T$ directly, we are in danger of replicating the problems arising for Takens.

@@

\chapter{Implementation} \label{sect5}
